A Case Study in Preserving a High Energy Physics Application

### 2014-01-20 paper.tex
format modification

\begin{figure}
\centering
\epsfig{file=data-process.eps, height=3in, width=3in}
\caption{Data Process}
\label{fig:data-process}
\end{figure}

The data process is shown in Figure~\ref{fig:data-process}.

@@

\subsection{Workflow of Matthias's Example}
Declare environment variables

Obtain software from CMSSW

Obtain software from Git

Obtain software from some public HTTP web links

Obtain software from one private home page

Build software enviroment using SCRAM and Python

Install grid control, obtain CMS data from grid and store the data into HDFS mounted as one local file system.

Actual data analysis.

\subsection{Source and Size of Data and Software}
We notice that the software sources are rich, including CMSSW, Git, HTTP and one personal main page. The size of software from each source is shown in Table~\ref{table:software-source-size}.

@@

\begin{figure*}
\centering
\epsfig{file=overview-of-architecture.eps, height=6in, width=7in}
\caption{Overview of Architecture}
\label{fig:Overview of architecture}
\end{figure*}

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        Version 1\\ \hline
        \\
        1. Create CMS release,\\
            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3... \\
        2. Install BEAN packages: \\
            \hspace{9pt} https://github.com/cms-ttH/...\\
        3. Install grid-control: \\ 
            \hspace{9pt} svn co https://dwekptrack... \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} git clone https://github.com/matz-e/... \\
           \hspace{9pt} scram b -j32 \\
        5. fix grid\_control.cfg and run it. \\
        6. Perform actual analysis \\ 
        \\ \hline
        Version 2\\ \hline
        \\
        set CMSSW\_BASE = (CMSSW\_5\_3...) \\
        module load git \\        
        cmsenv \\ 
        cvs login \\
        cvs co UserCode/Bicocca/... \\
        git clone... \\
        scram b -j32 \\
        wget http://pyyaml.org/... \\
        python setup.py install... \\
        \#the experiment data is from HDFS \\
        roaster data/generic\_ttl.yaml \\ 
        \\ \hline
        Version 3\\ \hline
        \\
        \#the description of OS version and hardware architecture \\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\ 
        cmsenv \\
        wget http://pyyaml.org/... \\
        python setup.py install... \\
        roaster data/generic\_ttl.yaml \\
        \\ \hline
        Version 4\\ \hline
        \\
        \#the description of OS version and hardware architecture \\
        \#declaration of environment variables\\
        \#clear data dependency\\
        \#clear software dependency\\
        \#software build and install command\\
        \#actual analysis program\\ 
        \\ \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

\section{Solution 1 to Repeat the Program}
In order to repeat Matthais's example, the new user consulted the original author by email about the necessary work for the experiment. In response, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links. The First version of Table~\ref{table:scripts} illstrates his email.

However, this solution to repeat one experiment has three potential drawbacks. Firstly, the experience of repeating one tau analysis through emails is chaotic. You need constant jumps around multiple web links. There are overlap between the content of the email and the content of web links, which needs the new user to merge them. Multiple communication through emails is necessary to ensure the successful repeat of the whole analysis. For example, the original email refers to one environment variable called CMSSW\_base without clear declaration, the new user needs to send one email to the original writer to obtain its accurate value. Secondly, the necessary procedure to repeat the experiment, including software acquisition from different sources, is complex for the new user. In Matthias's example, the sources of software includes CMSSW, Git, HTTP. The access of CMSSW requires the new user be an authorized user of CMSSW. What's more, some parts of the workflow are unrepeatible. The third step of this experiment requires the new user owning the access authority to the Grid.

Implication: Directly repeating the experiment using the workflow and results by the original author is complex and difficult. Some extra work must be done to make the reproduction process easier.

@@

To test out these possible solutions, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, software acquisition from CMSSW, Git and other web resources, and software installation, ends with the execution of the actual analysis program. Version 2 of Table~\ref{table:scripts} illstrates the merged script. As for the data acquisition from the Grid, we directly use the local copy in HDFS to avoidrequiring the new user to obtain a grid certification.

The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}. According to Table~\ref{table:time-2nd}, about half of the total execution time is consumed to prepare relevant software environment.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Sub-Task & Time & Percentage \\ \hline
    Software preparation from CMSSW & 15min 30s & 25.27\% \\ \hline
    Software preparation from Git & 9s & 0.24\% \\ \hline
    Software preparation from Wget & 36s & 0.98\% \\ \hline
    Environment Build - SCRAM & 13min 20s & 21.74\% \\ \hline
    Environment Build - Python & 1s & 0.03\% \\ \hline
    Data analysis & 31min 44s & 51.74\% \\ \hline
    Total & 61min 20s & 100.00\% \\ \hline
    \end{tabular}
    \caption{Breakdown of Execution Time of Solution 2}
    \label{table:time-2nd}
\end{table}

@@

Implication: All the data and software involved in the experiment should be provided to the new user in the format of one self-contained package so that the multiple execution of the experiment from the same user only involve one time of data and software acquisition and environment building process. In addition, the requirement of the underlying OS and hardware should also be provided to the new user.

@@

Figure~\ref{fig:Overview of architecture} illustrates all the dependencies involved in the program, which can be divided into two categories: clear dependencies and implicit dependencies. Clear dependencies include data dependencies and direct software dependencies which can be extracted directly from the analysis program. Implicit dependencies include indirect software dependencies which is necessary for the successful execution of direct software dependencies and other implicit dependencies. For example, we know Git is one direct software dependency from the analysis program, which further depends on perl, python, rsync, openssh-clients and other packages. The analysis program accesses one file File1, which is one soft link file further referring to File2.

@@

\subsection{Working principle of Packaging Utility}
The difficulty of data access authority acquisition enforces us to find out one solution, in which the reproduction of the original analysis can be done without any external dependency. That is, one independent and self-contained package containing all the data and software dependencies is necessary. Someone may suggest that it should be the responsibility of the original author to generate the required package. However, letting the original author to provide the package which can be used by others to repeat the original experiment is unrealistic. One reason is that figuring out the underlying dependency of each software is complex and time-consumpting and even impossible for the original author. In this experiment, the machine used for the experiment is one public machine of physics department, and Matthias is one common user without root authority. The underlying OS and supporting softwares are installed and maintained by the IT department of the university. On the other hand, the architecture design of the required package including all the data and software dependencies is not under the research field of physists.

Parrot is a virtual filesystem access tool which attaching existing programs to a variety of remote I/O systems including http, ftp, gridftp, irods, HDFS, xrootd, grow and chirp. it traps all system calls of one program through ptrace debugging interface, and replaces them with remote I/O operations as desired. through executing one program under parrot, all the paths of files involved in this program can be recorded.

With the help of parrot, one packaging utility which generates one independent package for one program to make the reproduction of the program convenient can be deployed. The basis of the packaging utility is one successful execution sandbox (the data from grid has been preserved in HDFS and the software from CMSSW, Git and HTTP has been on the local machine.). We re-execute the actual data analysis code under Parrot and get the name list of all the files actually accessed during the execution process of the actual data analysis. Then, according to the file name list, one package containing all the necessary data and software for one analysis program is generated. Next time, when another scholar wants to repeat the program, he only needs to obtain the package and directly execute the actual analysis program inside the package.

The shell script of the Solution 2 is simplified into one new version, which only contains the necessary environment variables, access authority and the actual analysis command. The Version 2 of Table~\ref{table:scripts} illustrates the simplified script.

\subsection{Workflow of Packaging Utility}
The workflow of generating one package for one analysis program is as follows:

@@

parrot\_run -l namelist /bin/tcsh parrot\_cms.sh

Output:
namelist size: 5.7MB     128711 lines

de-duplicated namelist size: 2.2MB   42385 lines

@@

The packaging utility iterates each filename inside L1 and copies it into the target package. After completing the packaging process, the target package together with its description information, and one mountlist, which redirects the access of data from different file systems into the target package, will be provided to users. The packaging process also runs within Parrot environment to access data from different file systems.

parrot\_run /bin/bash package1-4.sh -l ~/namelist

the path of pacakge is: /tmp/package1-4

the total size of package is: 21GB

the total number of files is: 1204

the total number of directory is: 473

the total number of symbolic link files is: 195

the mountlist path is: /tmp/mountlist

@@

To ensure the successful reproduction, the filesystem structure of the original execution environment should be preserved as completely as possible. However, attempting to copy the whole content of one directory or one file is space-consuming and time-consuming, because the original program may only access the metadata of one directory with the size of 200GB. our solution is to determine the copy degree of one directory or one common file according to the system call type for its path.

The map relationship between the file access path used in the actual analysis program and the actual file location used during the reproduction process is kept inside the mountlist file. the structure of the mountlist is as follows:

/ /tmp/package1-4

/tmp/package1-4 /tmp/package1-4

/dev /dev

/misc /misc

/net /net

/proc /proc

/sys /sys

/var /var

/selinux /selinux

@@

When another scholar wants to repeat one analysis program, the accessed data field is limited into the target package with the help of the mountlist generated in step 2.

@@

\begin{figure}
\centering
\epsfig{file=solution3.eps, height=3in, width=3in}
\caption{Relationship of Roles}
\label{fig:solution3}
\end{figure}

The relationship of different roles involved experiment preservation and reproduction is shown in Figure~\ref{fig:solution3}.
The original author is responsible for generating one package based on the successful execution sandbox with the help of the packaging utility. Then the package, together with the map file and description file will be uploaded into the archive. When another scholar wants to repeat the experiment, one copy of the package and its corresponding map file will be downloaded into the new machine.

@@

In the map relationship shown above, During the packaging process, we noticed
that it is impossible to copy the files under certain directories like /dev.
For example, during namelist acquisition process, three special files under /dev directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
We tried to copy these files into the new package, but the packaging utility halted.
We also noticed that copying the files under directories like /proc is
meaningless. Because the process id of one program is random and depends on the
current allocation of process ID. As for these two file categories, letting
the program directly utilize the files on the machine, where the new user
repeats the program, is a better choice. The semantics is implemented by
setting the target path of one file equal to the origin file path inside the
map file. For example, "/dev /dev" means that when the program needs to access
files under /dev directory, it will directly use the file under /dev, which is
independent from the namespace of the package. This semantics also makes the
reference of files outside the package possible. If the new user wants to
expand the analysis of one program to his own data with the path of /A, he can add the analysis
code into the analysis script and add one item "/A /A" into the map file.

@@

The data size of Solution 3 is shown in Table~\ref{table:datasize-3rd}. The data categories is more complex than our imagination. Except the data stored in Hadoop and the necessary set of software, files from /sbin, /bin and other paths are also necessary for the reproduction of the program.

@@

Under Solution 3, the reproduction of one analysis program becomes easier.
Rethink Matthias's example, the reproduction of it only needs
the necessary environment variables, svn login, the actual analysis command
and the package. If different scholars want to repeat one analysis program,
what they need to do is to obtain the package and rerun the actual analysis
program. Under Solution 2, each scholar needs to get the necessary data and
software, and then prepare software environment.

%here is the new content-hmeng
The starting point of Solution 3 is one successful execution sandbox on the original machine. 
Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one new package.
The necessary scientific data will be copied into the target package.
The software dependencies can be divided into two categories: clear dependencies, which can be observed directly through reading the analysis script and implicit dependencies,
which can not be obtained through reading the analysis script. 
Parrot can obtain every dependency through trapping each system call.
Strictly speaking, the software concept and the scientific data concept are lost in Solution 3, because
the granularity of parrot is file.
The same thing happens to network resources.
Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
As for the computing environment, Solution 3 notices the new user through the description information at the beginning of the script.
%the following subsection belongs to the "discussion of data and software
%preservation" section

@@

%*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software. if changed, one new package is generated to avoid data overlap and pollution. otherwise, directly starts packaging process based on the current target package. 
\section{Comparison of different Solutions}
\subsection{Relationship of Different Solutions}
The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}.

\subsection{ Data size Comparison of Solution 2 and 3}
The packaging utility checks the system call of each file within the namelist, and maintains the minimum dataset, which makes the size of the final package is as small as possible. The total size of Hadoop under Solution 2 is astonishing, while the size of Hadoop under the package is decreased to 20GB. The same trend applies to the size of CMSSW\_5\_3\_11\_patch3. Because the packaging utility tries to construct one independent and self-contained package, necessary files  from /sbin, /lib and other directories are also copied into the package and denoted as "Other data for Package" in the Table~\ref{table:datasize-2nd3rd}.

@@

\subsection{Execution Time Comparison of Solution 2 and 3}
Table~\ref{table:time-2nd3rd} shows the execution time comparison between Solution 2 and 3. The time consumption of the reproduction of one program from different scholars kept the same under Solution 2, including software and data preparation. However, under Solution 3, the data and software preparation is one-time. The following reproduction of the same program only needs to obtain one copy of the package and execute the actual experimental analysis directly.

@@

\begin{figure*}
\centering
\epsfig{file=preservation-integration.eps, height=4in, width=6in}
\caption{Preservation Integration of Multiple Programs}
\label{fig:Preservation integration}
\end{figure*}

To integrate the data and software from multiple analysis programs into one package, the concrete information of data and software, such as size, version, source and the number of files, need to be recorded. we also need to design one more instructive shell script format, in which the data dependencies and software dependencies can be clearly expressed and recognized. The packaging process needs to be re-organized. packaging utility needs to maintain one list of current software and data subset already stored in the package. When one user wants to generate one package, it will fork the packaging utility, the packaging utility will scan the script, get the data and software dependency part, judge whether each dependency has been inside the package, and only add the new data and software into the package, and update the package information and relavant retrieval information.

The architecture of preservation integration of multiple programs is shown in ~\ref{fig:Preservation integration}. Script 1 and Script 2, sharing one same dependency B, belongs two different programs. Without preservation integration, B will be preserved twice in the archive, which is space-consuming. To improve the utilization efficiency of storage resources, preservation integration of multiple programs is necessary. In the archive, only one copy of B is stored, which is referred by both scripts 1 and script 2.

\subsection{Preservation Granularity}
Another important factor of data and software preservation is the choice of preservation granularity. In Solution 3, the preservation granularity is one file, because Parrot virtual filesystem traps each system call and redirects the access path to each file. As a result, during the packaging process, each time only one file can be copied into the target package, which is low-efficient. However, there are other options of preservation granularity. The software is generally preserved in the unit of package inside the remote repository, the packaging process of one experiment can adopt one package as the unit. In addition, if the size of one whole software repository is small and the access frequency of each package inside it is high, the granularity can be set to the whole repository.

@@

The preservation policy must concern about the size of data. If its size is
small, copying it into one pacakge and transferring it between different
machines is not a bad idea.Howerver, when the size becomes large, copying it
into one package will make the size of the package uncontrollable.  In
Figure~\ref{fig:Preservation integration}, the size of C is very large and
easily to be obtained through Internet by different users. Directly referring C
as network resources is more efficient than preserving it into one package.

@@

The mining degree of data and software dependencies greatly determines the
repeatability of one experiment. Data dependencies is easy to figured out.
However, the situation of software dependencies is complex. The software
dependencies include OS, hardware platform, software directly forked inside the
progam and software indirectly forked by directly forked software. The first
three categories are easy to deal with. The description of indirect software
dependencies needs more efforts. One solution is to utlize package management
tools, like rpm, pacman, apt, to recursively trace each direct software
dependency and generate one clear dependency graph. With the dependency graph,
the new user can configure the software environment and repeat the experiment.
Solution 3 odopts this solution, which is easy to implement, but leaves the
complex environment configuration to the new users.

@@

Data and software preservation of physics experiments must concern the
preservation degree of the original filesystem.  The three core components of
one filesytem are file, directory and metadata.  The access of files can be
divided into two categories: only access file metadata, like size, ownership,
access authority list, and access both the file content and metadata.  If both
the content and metadata need to be accessed, the whole file must be copies
into the package.  However, if only the metadata of one file is accessed, how
to preserve the file needs to be considered carefully. If the size of the file
is 1KB or 1MB, preserving the content is acceptable. If the size of one file is
1GB, preserving the whole file just for the access of its metadata is
inefficient.

>>>>

\begin{figure}
\centering
\epsfig{file=data-process.eps, height=2.8in, width=3in}
\caption{Data Processing Procedures}
\label{fig:data-process}
\end{figure}

The data processing procedures are shown in Figure~\ref{fig:data-process}.

@@

\subsection{Workflow of Matthias's Example}

The workflow of Matthias's exmaple can be divided into eight procedures.

(a) Declare environment variables

(b) Obtain software from CMSSW

(c) Obtain software from Git

(d) Obtain software from some public HTTP web links

(e) Obtain software from one private home page

(f) Build software enviroment using SCRAM and Python

(g) Install grid control, obtain CMS data from grid and store the data into HDFS mounted as one local file system.

(h) Actual data analysis.

\subsection{Source and Size of Data and Software}

The software sources are rich, including CMSSW, Git, HTTP and one personal main page. The size of software from each source is shown in Table~\ref{table:software-source-size}.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|}
        \hline
        Version 1\\ \hline
        \\
        1. Create CMS release,\\
            \hspace{9pt} e.g. cmsrel CMSSW\_5\_3... \\
        2. Install BEAN packages: \\
            \hspace{9pt} https://github.com/cms-ttH/...\\
        3. Install grid-control: \\ 
            \hspace{9pt} svn co https://dwekptrack... \\
        4. INstall the TauAnalysis package: \\
           \hspace{9pt} git clone https://github.com/matz-e/... \\
           \hspace{9pt} scram b -j32 \\
        5. Fix grid\_control.cfg and run it. \\
        6. Perform actual analysis \\ 
        \\ \hline
        Version 2\\ \hline
        \\
        set CMSSW\_BASE = (CMSSW\_5\_3...) \\
        module load git \\        
        cmsenv \\ 
        cvs login \\
        cvs co UserCode/Bicocca/... \\
        git clone... \\
        scram b -j32 \\
        wget http://pyyaml.org/... \\
        python setup.py install... \\
        \#the experiment data is from HDFS \\
        roaster data/generic\_ttl.yaml \\ 
        \\ \hline
        Version 3\\ \hline
        \\
        \#the description of OS version and hardware architecture \\
        \# list of indirect software dependencies \\
        set CMSSW\_BASE = (CMSSW\_5\_3\_11\_patch3) \\ 
        cmsenv \\
        wget http://pyyaml.org/... \\
        python setup.py install... \\
        roaster data/generic\_ttl.yaml \\
        \\ \hline
        Version 4\\ \hline
        \\
        \#the description of OS version and hardware architecture \\
        \#declaration of environment variables\\
        \#data dependencies\\
        \#direct and indirect software dependencies\\
        \#software build and install commands\\
        \#actual analysis program\\ 
        \\ \hline
    \end{tabular}
    \caption{Scripts of each Solution}
    \label{table:scripts}
\end{table}

\section{Solution 1 to Repeat the Program}
In order to repeat Matthais's example, the new user consulted the original author by email about the necessary work for the experiment. In response, Matthias introduced the general workflow of his tau analysis through one long email including notes, linux shell commands, web links. The Version 1 of Table~\ref{table:scripts} illstrates his email.

However, this solution to repeat one experiment has three potential drawbacks.
Firstly, the experience of repeating one tau analysis through emails is
chaotic. You need to constantly jump around multiple web links. There are overlap
between the content of the email and the content of web links, which needs the
new user to merge them. Multiple communication through emails is necessary to
ensure the successful reproduction of the whole analysis. For example, the original
email refers to one environment variable called CMSSW\_base without clear
declaration, the new user needs to send one email to the original writer to
obtain its accurate value. Secondly, the necessary procedures to repeat the
experiment, including software acquisition from different sources, is complex
for the new user. In Matthias's example, the sources of software includes
CMSSW, Git, HTTP. The access of CMSSW requires the new user to be an authorized
user of CMSSW. What's more, some parts of the workflow are unrepeatable. The
third step of this experiment requires the new user to own the access authority
of the Grid.

Implication: Directly repeating the experiment using the workflow description and results provided by the original author is complex and difficult. Some extra work must be done to make the reproduction process easier.

@@

To test out these possible solutions, we integrate the content of all the notes, commands and web links involved in the emails into one neat, complete shell script, which begins with the definition of environment variables, software acquisition from CMSSW, Git and other web resources, and software installation, ends with the execution of the actual analysis program. Version 2 of Table~\ref{table:scripts} illstrates the merged script. As for the data acquisition from the Grid, we directly use the local copy in HDFS to avoid requiring the new user to obtain a grid certification.

The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}. About half of the total execution time is consumed to prepare relevant software environment. The cvs command is forked to check out 23 packages from CMSSW and three git repositories are cloned.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Sub-Task & Time & Percentage \\ \hline
    Software acquisition from CMSSW & 15min 30s & 25.27\% \\ \hline
    Software acquisition from Git & 9s & 0.24\% \\ \hline
    Software acquisition from Wget & 36s & 0.98\% \\ \hline
    Environment Build - SCRAM & 13min 20s & 21.74\% \\ \hline
    Environment Build - Python & 1s & 0.03\% \\ \hline
    Data analysis & 31min 44s & 51.74\% \\ \hline
    Total & 61min 20s & 100.00\% \\ \hline
    \end{tabular}
    \caption{Breakdown of Execution Time of Solution 2}
    \label{table:time-2nd}
\end{table}

@@

Implication: All the data and software involved in the experiment should be
provided to the new user in the format of one self-contained package so that
the new user can avoid complex data and software acquisition and software
environment building process. In addition, the requirements of the underlying
OS and hardware should also be provided to the new user.

@@

\begin{figure*}
\centering
\epsfig{file=overview-of-architecture.eps, height=4in, width=6.5in}
\caption{Overview of Architecture}
\label{fig:Overview of architecture}
\end{figure*}

Figure~\ref{fig:Overview of architecture} illustrates all the dependencies
involved in the program, which can be divided into two categories: clear
dependencies and implicit dependencies. Clear dependencies include data
dependencies and direct software dependencies which can be extracted directly
from the analysis program. Implicit dependencies include indirect software
dependencies which is necessary for the successful execution of direct software
dependencies and other implicit dependencies. For example, we know Git is one
direct software dependency from the analysis program, which further depends on
perl, python, rsync, openssh-clients and other packages. The analysis program
accesses one file called File1, which is one soft link file further referring to
another name named File2. 
The implicit dependencies also refers to some files under /pscratch, which is one local mount point of one PanFS clustered file system with the size of 206TB.

@@

\subsection{Working principle of Packaging Utility}

The difficulty of data access authority acquisition enforces us to find out one
solution, in which the reproduction of the original analysis can be done
without any external dependency. That is, one independent and self-contained
package containing all the data and software dependencies is necessary.

Someone may suggest that it should be the responsibility of the original author
to generate the required package. However, letting the original author provide
the package which can be used by others to repeat the original experiment is
unrealistic. One reason is that figuring out the underlying dependencies of
each software is complex and time-consumpting and even impossible for the
original author. In this experiment, the machine used for the experiment is one
public machine of physics department, and Matthias is one common user without
root authority. The underlying OS and supporting softwares are installed and
maintained by the IT department of the university. On the other hand, the
architecture design of the required package including all the data and software
dependencies is not under the research field of physists.

Parrot is a virtual filesystem access tool which attaching existing programs to
a variety of remote I/O systems including http, ftp, gridftp, irods, HDFS,
xrootd, grow and chirp. It traps all system calls of one program through ptrace
debugging interface, and replaces them with remote I/O operations as desired.
Through executing one program under Parrot, all the paths of files involved in
this program can be recorded.

With the help of Parrot, one packaging utility which generates one independent
package for one program to make the reproduction of the program convenient can
be deployed. The starting point of the packaging utility is one successful execution
sandbox (the data from grid has been preserved in HDFS and the software from
CMSSW, Git and HTTP has been on the local machine.). We re-execute the actual
data analysis code under Parrot and get the name list of all the files actually
accessed during the execution process of the actual data analysis. Then,
according to the file name list, one package containing all the necessary data
and software for one analysis program is generated. Next time, when another
scholar wants to repeat the program, he only needs to obtain the package and
directly execute the actual analysis program inside the package.

The shell script of the Solution 2 is simplified into one new version, which
only contains the necessary environment variables, access authority and the
actual analysis command. The Version 3 of Table~\ref{table:scripts} illustrates
the simplified script.

\subsection{Workflow of Packaging Utility}
The workflow of generating one package for one analysis program is as follows.

@@

The command used to generate the file name list is as follows. The `-L` parameter refers to the path of the file containing all the accessed file name of the experiment.

parrot\_run -L namelist /bin/tcsh parrot\_cms.sh

The original ouput of this command is one namelist file with the size of 5.7MB
and 128,711 lines, each of which corresponds to one one accessed file of the
program. We noticed that some items appeared multiple times. To reduce the
packaging time, de-duplication and sorting techoniques are used for the
namelist file, generating one smaller file with the size of 5.7MB and 42,385
lines.

@@

The packaging utility iterates each filename inside L1 and copies it into the
target package. After finishing the packaging process, the target package
together with its description information, and one map file, which redirects
the access of files from different file systems into the files inside the target package, will be
provided to users. The packaging process also runs within Parrot environment to
access data from different file systems.

\begin{figure}
\centering
\epsfig{file=package-info.eps, height=1.5in, width=2.5in}
\caption{Package Description Infomation}
\label{fig:package-info}
\end{figure}
The command used to generate the package containing all the files of L1 is as follows. 
`package1-4.sh` is a bash script which iterates each line of L1 and
determines the behavior according to the file type (common files, directories,
linked files) and the system call type.
The package description information is shown in Figure~\ref{fig:package-info}.

parrot\_run /bin/bash package1-4.sh -L ~/namelist

@@

To ensure the successful reproduction, the filesystem structure of the original
execution environment should be preserved as completely as possible. However,
attempting to copy the whole content of one directory or one file is
space-consuming and time-consuming, because the original program may only
access the metadata of one file with the size of 200GB. Our solution is to
determine the copy degree of one directory or one common file according to the
system call type for its path.

The map relationship between the file access path used in the actual analysis
program and the actual file location used during the reproduction process is
kept inside the map file. The structure of the map file is shown in Table~\ref{table:map-file}.

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
    Path used in Program & Actual Location \\ \hline
    / & /tmp/package1-4 \\ \hline
    /tmp/package1-4 & /tmp/package1-4 \\ \hline
    /dev & /dev \\ \hline
    /misc & /misc\\ \hline
    /net & /net\\ \hline
    /proc & /proc\\ \hline
    /sys & /sys\\ \hline
    /var & /var\\ \hline
    /selinux & /selinux\\ \hline
    \end{tabular}
    \caption{Structure of Map File}
    \label{table:map-file}
\end{table}

@@

When another scholar wants to repeat one analysis program, the accessed data
field is limited into the target package with the help of the map file 
generated in step 2.

@@

\begin{figure}
\centering
\epsfig{file=solution3.eps, height=2in, width=3in}
\caption{Relationship of Roles}
\label{fig:solution3}
\end{figure}

The relationship of different roles involved experiment preservation and
reproduction is shown in Figure~\ref{fig:solution3}.  The original author is
responsible for generating one package based on the successful execution
sandbox with the help of the packaging utility. Then the package, together with
its map file and description file will be uploaded into the archive. When
another scholar wants to repeat the experiment, one copy of the package and its
corresponding map file will be downloaded into the new machine.

@@

During the packaging process, we noticed
that it is impossible to copy the files under certain directories.
For example, during namelist acquisition process, three special files under /dev directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
We tried to copy these files into the new package, but the packaging utility halted.
We also noticed that copying the files under directories like /proc is
meaningless. Because the process id of one program is random and depends on the
current allocation of process ID.

As for these two file categories, letting
the program directly utilize the files on the machine, where the new user
repeats the program, is a better choice. The semantics is implemented by
setting the target path of one file equal to the origin file path inside the
map file. For example, "/dev /dev" means that when the program needs to access
files under /dev directory, it will directly use the file under /dev, which is
independent from the namespace of the package. This semantics also makes the
reference of files outside the package possible. If the new user wants to
expand the analysis of one program to his own data with the path of /A, he can add the analysis
code into the analysis script and add one item "/A /A" into the map file.

@@

The data size of Solution 3 is shown in Table~\ref{table:datasize-3rd}. The
data categories is more complex than our imagination. Except the data stored in
Hadoop and the necessary set of software, files from /pscratch, /sbin, /lib and other
paths are also necessary for the reproduction of the program.

@@

Under Solution 3, the reproduction of one analysis program becomes easier.
Rethink Matthias's example, the reproduction of it only needs
the necessary environment variables, the actual analysis command
and the package. If different scholars want to repeat one analysis program,
what they need to do is to obtain the package and rerun the actual analysis
program. Under Solution 2, each scholar needs to get the necessary data and
software, and then prepare software environment.

%here is the new content-hmeng
The starting point of Solution 3 is one successful execution sandbox on the original machine. 
Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one package.
The necessary scientific data will be copied into the target package.
The software dependencies can be divided into two categories: clear dependencies, which can be observed directly through reading the analysis script and implicit dependencies,
which can not be obtained through reading the analysis script. 
Parrot can obtain every dependency through trapping each system call.
Strictly speaking, the software concept and the scientific data concept are lost in Solution 3, because
the granularity of parrot is file.
The same thing happens to networked resources.
Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
As for the computing environment, Solution 3 notices the new user through the description information at the beginning of the script.
%the following subsection belongs to the "discussion of data and software
%preservation" section

@@

%*****hmeng-doubt: in the fourth version, let user to mark whether they change the data and software. if changed, one new package is generated to avoid data overlap and pollution. otherwise, directly starts packaging process based on the current target package. 
\section{Comparison of different Solutions}
\subsection{Relationship of Different Solutions}
The relationship of these three solutions to repeat one program is shown in Table~\ref{table:relationship}. The aim is to make it easier to repeat one program through making the data and software preparation easier.

\subsection{ Data size Comparison of Solution 2 and 3}

The packaging utility checks the system call of each file within the namelist,
and maintains the minimum dataset, which makes the size of the final package 
as small as possible. The total size of Hadoop under Solution 2 is astonishing,
while the size of Hadoop under the package is decreased to 20GB. The same trend
applies to the size of CMSSW\_5\_3\_11\_patch3. Because the packaging utility
tries to construct one independent and self-contained package, necessary files
from /sbin, /lib and other directories are also copied into the package and
denoted as "Other data for Package" in Table~\ref{table:datasize-2nd3rd}.

@@

\subsection{Execution Time Comparison of Solution 2 and 3}

Table~\ref{table:time-2nd3rd} shows the execution time comparison between
Solution 2 and 3. The time consumption of the reproduction of one program from
different scholars kept the same under Solution 2, including software and data
preparation. However, under Solution 3, the data and software preparation is
one-time. The following reproduction of the same program only needs to obtain
one copy of the package and execute the actual experimental analysis directly.
Data is obtained through accessing Hadoop Distributed File System in Solution 2, but is copied into the package in Solution 3. This localization of data speeds up the data analysis process, resulting the actual analysis time reducing from 31 minutes to 13 minutes.

@@

\begin{figure}
\centering
\epsfig{file=preservation-integration.eps, height=2.2in, width=3.3in}
\caption{Preservation Integration of Multiple Programs}
\label{fig:Preservation integration}
\end{figure}

To integrate the data and software from multiple analysis programs into one
package, the concrete information of data and software, such as size, version,
source and the number of files, need to be recorded. we also need to design one
more instructive shell script format, in which the data dependencies and
software dependencies can be clearly expressed and recognized. The packaging
process needs to be re-organized. Packaging utility needs to maintain one list
of current software and data subset already stored in the package. When one
user fork the packaging utility to preserve one program, the
packaging utility will scan the script, get the data and software dependency
part, judge whether each dependency has been inside the package, and only add
the new data and software into the package, and update the package information
and relavant retrieval information.

The architecture of preservation integration of multiple programs is shown in
Figure~\ref{fig:Preservation integration}. Script 1 and Script 2, sharing one
dependency B, belongs two different programs. Without preservation
integration, B will be preserved twice in the archive, which is
space-consuming. To improve the utilization efficiency of storage resources,
preservation integration of multiple programs is necessary. In the archive,
only one copy of B is stored, which is referred by both scripts and script 2.

\subsection{Preservation Granularity}

Another important factor of data and software preservation is the choice of
preservation granularity. In Solution 3, the preservation granularity is one
file, because Parrot virtual filesystem traps each system call and redirects
the access path of each file. As a result, during the packaging process, each
time only one file can be copied into the target package, which is
low-efficient. However, there are other options of preservation granularity.
The software is generally preserved in the unit of package inside the remote
repository, the packaging process of one experiment can adopt one package as
the unit. In addition, if the size of one whole software repository is small
and the access frequency of each package inside it is high, the granularity can
be set to the whole repository.

@@

The preservation policy must concern about the size of data. If its size is
small, copying it into one pacakge and transferring it between different
machines is not a bad idea. Howerver, when the size becomes large, copying it
into one package will make the size of the package uncontrollable. In
Figure~\ref{fig:Preservation integration}, the size of C is very large and
easily to be obtained through Internet by different users. Directly referring C
as networked resources is more efficient than preserving it into one package.

@@

The mining degree of data and software dependencies greatly determines the
repeatability of one experiment. Data dependencies is easy to figured out. However, the situation of software dependencies is complex. The software
dependencies include OS, hardware platform, 
direct software dependencies and indirect software dependency which is dependent upon direct software dependencies.
The first
three categories are easy to deal with. The description of indirect software
dependencies needs more efforts. One solution is to utlize package management
tools, like rpm, pacman, apt, to recursively trace each direct software
dependency and generate one clear dependency graph. With the dependency graph,
the new user can configure the software environment and repeat the experiment.
Solution 3 odopts this solution, which is easy to implement, but leaves the
complex environment configuration to the new users.

@@

Data and software preservation of physics experiments must concern the
preservation degree of the original filesystem.  The three core components of
one filesytem are file, directory and metadata.  The access of files can be
divided into two categories: only access file metadata, like size, ownership,
access authority list, and access both the file content and metadata.  If both
the content and metadata need to be accessed, the whole file must be copies
into the package.  However, if only the metadata of one file is accessed, how
to preserve the file needs to be considered carefully. If the file size
is 1KB or 1MB, preserving the content is acceptable. If the size of one file is
1GB, preserving the whole file just for accessing its metadata is
inefficient.

Directory is one list of files and subdirectories under it. At first, we only
copied the accessed items under one directory and ignored the unaccessed items.
However, some operations on one directory depends on each item under it. For
example, `ls /dirA` is one linux command to list the name of each item under
/dirA. Because the directory itself has the name list of items under it, only
the path of the directory was recorded into the namelist in the first phrase of
Solution 3. However, when we repeated the command `ls /dirA` using the
preserved package, it returned NULL because none of items under it existed in
the package. If one routine within the original program depends on the return
value of `ls /dirA`, the behavior of the whole program will become incorrect
and unpredictable.
